Refinements for open automata

### 2021-12-10 2021-Refinement/paper/refinementarticle.tex
debut preuve thm2

On one side, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exist an indexed family of OTs originating from $s_{2p}$: 
\begin{align*}
\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
\end{align*}
such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} 
\end{multline*}		
that can be re-written:
\begin{multline*}
%\everymath{\displaystyle}
\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} \\
	\end{multline*}	
\medskip
Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \land\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
		\end{array}} \\
\end{align*}

@@

We have:

@@

This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition \TODO{re-write the set of OTs or not?} with note that $\psi_{2px}$ has no effect on variables of $A1$ and $A3$:

@@

\TODO{[LUDO] je suis un peu embete par le fait qu on se soit debarrasse des quantifiers et qu ils reviennent miraculeusement ici, a completer ou au moins commeter a mon avis (1footnote peut suffire si on est bien convaincus)}

@@

\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:

@@

\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{j \in J'_{2p}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}

@@

\section{Proof of Context Refinement}

>>>>

On one side, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exist an indexed family of OTs originating from $s_{2p}$: 
\begin{align*}
\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
\end{align*}
such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} 
\end{multline*}		
that can be re-written:
\begin{multline*}
%\everymath{\displaystyle}
\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} \\
	\end{multline*}	
\medskip
Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: \footnote{Note for the sake of readability, when we justify each step in a a proof
we omit to rewrite the quantification over of formula which remains unchanged.}
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \land\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
		\end{array}} \\
\end{align*}

@@

Indeed, we have:

@@

This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition  with note that $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$:

@@

@@

\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:

@@

\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{\begin{array}{c} p\in P\\ j \in J'_{2p}
\end{array}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}

@@

\section{Proof of Context Refinement}
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
Let us define $R'$ the relation:
\[R' \mpar{\mpar{s_{13}, s'_{13}}, \mpar{s_{23}, s_{23}'}} = \choice{R\mpar{s_{13}, s_{23}} \wedge \reach{A_{13}}\mpar{s_{13},s_{13}'} \wedge\!\!\!\! \bigwedge_\subbox{\begin{array}{c}
v\in \fvars{s'_{13}}\\
v\in V_3
\end{array}}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s'_{13} = s'_{23} \\ \bot & \text{otherwise}} \]
We want to prove that $\mpar{R, H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
\begin{enumerate}
\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial state is reachable and renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

We have by hypothesis:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
v\in V_3
\end{array}} \sigma_{03}(v)=\sigma_{03}(v)\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
v\in V_3
\end{array}} \sigma_{013}(v)=\sigma_{023}(v)
\end{align*}

\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
